\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-17 paper/sp.tex
CMD

For training, we need A and B Training Sets.
We define the Training Set stars to be Parent-Sample stars that also
have a measured \gaia\ parallax.
The Training-Set stars, in addition to meeting all Parent-Sample cuts,
also must meet an uncertainty criterion $\gsigma_n < 0.1\,\mathrm{mas}$,
\begin{equation}
\code{parallax_error < 0.1}
\end{equation}
it must be observed by more than $8$ (widely separated) times
\begin{equation}
\code{visibility_periods_used >= 8}
\end{equation}
as well as meet the additional quality criterion
\begin{equation}
\code{astrometric_chi2_al / sqrt(astrometric_n_good_obs_al - 5) <= 35}
\end{equation}
which eliminates detections that are not consistent with a single PSF \citep[see][]{calj},
to ensure that the parallax measurements are good.
These cuts leave 28226 stars total in the Training Sets.
But---as we have emphasized above---we do not cut ever on parallax or
or the ratio to its uncertainty. For this reason, most of the Training-Set stars
do not have significantly measured parallaxes and more than 2~percent even have
negative parallaxes!
But we will perform our training such that it will be unbiased in these
circumstances.
Indeed it would be necessarily biased if ever we did cut on parallax or
parallax signal-to-noise.

@@

Finally, one comment on the use of these spectroscopic parallaxes.
They are noisy.
Precise use of these involves building a likelihood function and performing inference,
just as the precise use of the \gaia\ data presented here required the same.
We recommend making analogous inferences when using these outputs.

>>>>

For training, we need A and B Training Sets.
We define the Training Set stars to be Parent-Sample stars that also
have a measured \gaia\ parallax.
The Training-Set stars, in addition to meeting all Parent-Sample cuts,
also must meet an uncertainty criterion $\gsigma_n < 0.1\,\mathrm{mas}$, i.e. 
\begin{equation}
\code{parallax_error < 0.1}
\end{equation}
it must be observed by more than $8$ (widely separated) times
\begin{equation}
\code{visibility_periods_used >= 8}
\end{equation}
as well as meet the additional quality criterion
\begin{equation}
\code{astrometric_chi2_al / sqrt(astrometric_n_good_obs_al - 5) <= 35}
\end{equation}
which eliminates detections that are not consistent with a single PSF \citep[see][]{calj},
to ensure that the parallax measurements are good.
These cuts leave 28226 stars total in the Training Sets.
But---as we have emphasized above---we do not cut ever on parallax or
or the ratio to its uncertainty. For this reason, most of the Training-Set stars
do not have significantly measured parallaxes and more than 2~percent even have
negative parallaxes!
But we will perform our training such that it will be unbiased in these
circumstances.
Indeed it would be necessarily biased if ever we did cut on parallax or
parallax signal-to-noise.

@@

Finally, one comment on the use of these spectrophotometric parallaxes.
They are noisy.
Precise use of these involves building a likelihood function and performing inference,
just as the precise use of the \gaia\ data presented here required the same.
We recommend making analogous inferences when using these outputs.
